\Title

### 2020-07-24 manuscript/manuscript.tex
Finish introduction

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{booktabs}

@@

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
biharmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
These general-purpose methods have limitations when it comes to interpolating
potential field data:
(i) they are not able to take into account the variable height of the
observation points and
(ii) the interpolating functions are not necessarily harmonic functions, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).

A widely used method for interpolating gravity and magnetic data
is the equivalent source technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation), first introduced by
\citet{dampney1969}.
It consists in fitting a model of elementary sources to the data and using this
model to predict new data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{guspi2009, silva1986, emilia1973, nakatsuka2006}, upward
continuation (CITATION NEEDED), and merging datasets (CITATION NEEDED).

Many variants of the equivalent source technique have been proposed.
The key factors that vary between them are: (i) the type of source, (ii)
the location of the sources, and (iii) the solution strategy.
The type of source is most commonly a point mass (for gravity) or dipole (for
magnetics) (CITATION NEEDED).
However, an inverse distance function $1/r$ (CITATION NEEDED),
right-rectangular prisms \citep{barnes2011} (CITATION NEEDED:
one by the simpeg group and one for magnetic data integration),
and tesseroids \citep{bouman2016} have also been used successfully.
The sources are often distributed on a regular grid at a constant depth
\citep[e.g.,~]{barnes2011,oliveira2013}
(e.g., CITATION NEEDED) or placed beneath each data point (e.g., CITATION NEEDED).
The model is usually estimated through damped least-squares, which imposes a
heavy computational load when the number of data points is large (e.g.,
airborne and satellite surveys).
Other solution strategies have been proposed to attempt to reduce this load and
make the use of equivalent sources feasible.
\citet{mendonca1994} blablabla.
\citet{leao1989} blablabla.
\citet{li2010} blablabla.
\citet{barnes2011} blablabla.
\citet{oliveira2013} blablabla.
\citet{siqueira2017} blablabla.
\citet{jirigalatu2019} blablabla.
Many other techniques have been proposed, more so than could be included here.

In the present study, we will evaluate the impact of different source
distributions, both horizontally and vertically, on the performance of
equivalent source interpolation.
Vertically, the sources can be located: (i) at a constant depth, (ii) at a
depth relative to the height of observations, and (iii) at a depth
proportional to the median distance to adjacent data points.
The horizontal source distribution strategies are: (i) regular grid, (ii)
beneath data point, (iii) on the median location of data points inside spatial
blocks. The latter is a novel method while the others have been used in some
form in the past.

@@

The Green's equivalent layer theorem states that any harmonic potential field
generated by any three dimensional physical-property distribution can by
reproduced by a continuous two dimensional surface distribution.
This introduces an ambiguity on the distribution that generates
a potential field: multiple physical-property distributions can generate the
same potential field.
This represents an obstacle for determining the true shape and
physical-property distribution that generates any measured potential field.
Nevertheless this ambiguity can also be exploited for developing preprocessing
techniques like interpolating potential field data.

@@

Each source distribution from Table~\ref{tab:source-distributions} needs
certain parameters in order to build the set of point sources.
The prediction capabilities of the source distribution depends on the choice of
these parameters.
For example, locating the sources beneath the data points at constant depth
needs the definition of the \emph{depth} parameter.
If the sources are set too close to the data points, the source distribution
it's very likely to overfit the data: the measured field will be recovered, but
the predictions on unobserved locations will be very inaccurate.
Another parameter that plays an important role on the predictive capabilities
of the sources is the \emph{damping}.

@@

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                & \GroundGridSourcesConstantDepthDepth
                  \GroundGridSourcesConstantDepthDepthIncrement
                & \BestGroundGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestGroundGridSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundGridSourcesConstantDepthSpacing
                  \GroundGridSourcesConstantDepthSpacingIncrement
                & \BestGroundGridSourcesConstantDepthSpacing
                & \\
            &
                & Pad
                & \GroundGridSourcesConstantDepthPad
                  \GroundGridSourcesConstantDepthPadIncrement
                & \BestGroundGridSourcesConstantDepthPad
                & \\
            &
                & Damping
                & \GroundGridSourcesConstantDepthDamping
                  \GroundGridSourcesConstantDepthDampingIncrement
                & \BestGroundGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

@@

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                & \AirborneGridSourcesConstantDepthDepth
                  \AirborneGridSourcesConstantDepthDepthIncrement
                & \BestAirborneGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneGridSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneGridSourcesConstantDepthSpacing
                  \AirborneGridSourcesConstantDepthSpacingIncrement
                & \BestAirborneGridSourcesConstantDepthSpacing
                & \\
            &
                & Pad
                & \AirborneGridSourcesConstantDepthPad
                  \AirborneGridSourcesConstantDepthPadIncrement
                & \BestAirborneGridSourcesConstantDepthPad
                & \\
            &
                & Damping
                & \AirborneGridSourcesConstantDepthDamping
                  \AirborneGridSourcesConstantDepthDampingIncrement
                & \BestAirborneGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

@@

\bibliographystyle{plainnat}
\bibliography{references}

>>>>

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round,authoryear,sort]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{booktabs}

@@

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
These general-purpose methods have limitations when it comes to interpolating
potential field data:
(i) they are not able to take into account the variable height of the
observation points and
(ii) the interpolating functions are not necessarily harmonic functions, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).

A widely used method for interpolating gravity and magnetic data
is the equivalent source technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation), first introduced by
\citet{dampney1969}.
It consists in fitting a model of elementary sources to the data and using this
model to predict new data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{silva1986, nakatsuka2006, guspi2009}, upward
continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
data \citep{barnes2011}, modelling the lithospheric magnetic field
\citep{kother2015}, recovering the magnetic induction vector from
total-field magnetic anomalies \citep{li2020}, and more.

Many variants of the equivalent source technique have been proposed, often
attempting to obtain faster or more accurate solutions.
The key factors that vary between them are: (i) the type of source, (ii)
the location of the sources, and (iii) the solution strategy.
The type of source is most commonly a point mass (for gravity) or dipole (for
magnetics) \citep[e.g.,~]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
However, an inverse distance function $1/r$ \citep{cordell1992},
right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019, li2020},
and tesseroids \citep{bouman2016} have also been used successfully.
The sources are often distributed on a regular grid at a constant depth
\citep[e.g.,~]{leao1989, barnes2011, oliveira2013}
or placed beneath each data point \citep[e.g.,~]{cordell1992, siqueira2017}.
The model is usually estimated through damped least-squares, which imposes a
heavy computational load when the number of data points is large (e.g.,
airborne and satellite surveys).
To reduce the computational load, \citet{mendonca1994} built the solution
iteratively by incorporating one data point at a time using the ``equivalent
data concept''.
\citet{leao1989} processed the input data using a moving window, only fitting the
data inside the window and predicting observations at the center of the window.
\citet{li2010} and \citet{barnes2011} apply different operations to generate a
sparse representation of the sensitive matrix (respectively, wavelet
compression and quadtree discretization), which significantly improves the
speed of the least-squares solution.
\citet{oliveira2013} parametrized the equivalent layer as a piecewise bivariate
polynomial function, reducing the number of parameters in the solution.
\citet{siqueira2017} developed an iterative solution in which the sensitivity
matrix is transformed into a diagonal matrix with constant terms through the
``excess mass criterion''.
\citet{jirigalatu2019} applied the Guass-FFT method to speed up the forward
modelling operations and solved the least-squares problem using steepest
descent to avoid calculating the Hessian matrix and solving linear systems.
Most existing methods solve under-determined problems, requiring a much larger
number of equivalent sources than the number of data points.
Furthermore, many of the optimizations proposed are also complex to implement
in a computer program, limiting their wider adoption.

In the present study,
we propose a simple method for reducing the number of equivalent sources.
The survey area is divided into horizontal blocks and one source is assigned
to each block at the median horizontal location of the data points.
For airborne surveys, which are oversampled along tracks, this can greatly
reduce the size of the inverse problem while retaining the quality of
interpolation.
We experiment with the existing strategies of assigning sources at
a uniform depth, a depth relative to the data height, or a depth proportional
to the median distance to adjacent data points.
Through tests on synthetic data, we show that non-uniform depths perform better
at interpolation and that our method is able to achieve the same accuracy as a
traditional equivalent layer while using a fraction of the number of sources.

@@

The Green's equivalent layer theorem states that any harmonic potential field
generated by any three dimensional physical-property distribution can by
reproduced by a continuous two dimensional surface distribution.
This introduces an ambiguity on the distribution that generates
a potential field: multiple physical-property distributions can generate the
same potential field.
This represents an obstacle for determining the true shape and
physical-property distribution that generates any measured potential field.
Nevertheless this ambiguity can also be exploited for developing pre-processing
techniques like interpolating potential field data.

@@

Each source distribution from Table~\ref{tab:source-distributions} needs
certain parameters in order to build the set of point sources.
The prediction capabilities of the source distribution depends on the choice of
these parameters.
For example, locating the sources beneath the data points at constant depth
needs the definition of the \emph{depth} parameter.
If the sources are set too close to the data points, the source distribution
it's very likely to over-fit the data: the measured field will be recovered, but
the predictions on unobserved locations will be very inaccurate.
Another parameter that plays an important role on the predictive capabilities
of the sources is the \emph{damping}.

@@

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                & \GroundGridSourcesConstantDepthDepth
                  \GroundGridSourcesConstantDepthDepthIncrement
                & \BestGroundGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestGroundGridSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundGridSourcesConstantDepthSpacing
                  \GroundGridSourcesConstantDepthSpacingIncrement
                & \BestGroundGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundGridSourcesConstantDepthDamping
                  \GroundGridSourcesConstantDepthDampingIncrement
                & \BestGroundGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

@@

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                & \AirborneGridSourcesConstantDepthDepth
                  \AirborneGridSourcesConstantDepthDepthIncrement
                & \BestAirborneGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneGridSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneGridSourcesConstantDepthSpacing
                  \AirborneGridSourcesConstantDepthSpacingIncrement
                & \BestAirborneGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneGridSourcesConstantDepthDamping
                  \AirborneGridSourcesConstantDepthDampingIncrement
                & \BestAirborneGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

@@

\bibliographystyle{humannat}
\bibliography{references}
